\plaintitle

### 2018-04-05 paper/paper.tex
...

@@

\begin{figure}[h]
  % \includegraphics[width=10cm,bb=0 0 1290 866]{figures/githelp1.png}
  % \includegraphics[width=12cm,bb=-100 -100 1190 766]{figures/githelp1.png}
  \includegraphics[width=9cm,bb=0 0 1000 600]{figures/githelp1.png}
  \caption{Invoking {\GH}.}
  \label{bash1}
\end{figure}

Here, various candidate entries with
descriptios and command strings are listed.
One of the entries says ``README.mdをふたつ前のバージョンと比較する'',
which means ``to compare \tt{README.md} with the one from 2 versions before.''
%
If the user thinks that that's what he wants to do,
he can select the entry by selecting it by typing arrow keys
and type the enter key.
Then the user's input string is replaced by the right command string
that satisfies the user's need.

A description like ``2日前''(2 days ago) was also shown in the candidate list.
This means that the user can use the same string ``\tt{git RE 2}''
for getting the \tt{README.md} file of the day before yesterday.
The command,
``\verb|$ git diff '@{2 days ago}' README.md|'',
is difficult to remember,
but users can do the same thing only by saying \tt{RE} and \tt{2}.

A Japanese \tt{git} user can do the same thing just like
English-speaking users.

\begin{figure}[h]
  % \includegraphics[width=10cm,bb=0 0 1290 866]{figures/githelp1.png}
  \includegraphics[width=12cm,bb=-100 -100 1190 766]{figures/githelp1.png}
  \caption{Invoking {\GH}.}
  \label{bash2}
\end{figure}

If the user wants to know more about the command line options,
he can click the ``i'' button and browse the Wiki page.
The page can be edited by any user, and

(Figure of Wiki here)

@@

% \subsection{Translation}

@@

\begin{quote}
  description: \\
  \stt{Compare (\#{files}) with the one from (1|2|3|4) versions before}\\
  command: \\
  \stt{git diff ....}
\end{quote}

The first regular expression, the description part,
is for generating texts like
\qsf{Compare README.md with the one from 1 versions before}, 
\qsf{Compare index.html with the one from 2 versions before}, etc.,
and the second part, command part,
is used to generate a command to execute a \tt{git} command.
In the first example, \qsf{README.md} and \qsf{1}
match the first and second parentheses of the regular expression, and
these values are assigned to \tt{\$1} and \tt{\$2}
for the command part, generating a command
\tt{git xxxxxxx}.

@@

\subsection{(section written for GitHelp)}

{\EH} is a general-purpose flexible help generation system
that has the following characteristics.

\begin{itemize}
\item Use description-execution pairs for the translation
\item Standard regular expression is used for the specification of the description
\item The specification RegExp is expanded and filtered by the user's input string
  real-time
\end{itemize}

An example of the desc-exec pair can be the following:

\begin{verbatim}
  (delete|remove) a (#{file})
  /bin/rm $2
\end{verbatim}

``remove \verb|README.md|''
into
``\verb|rm README.md|

First, the spec like \stt{\#\{file\}} is expanded to a list of filenames like
\verb+README.md|Makefile|test.c+,
and the spec string becomes
``\verb+(delete|remove) a file (README.md|Makefile|test.c)+''.
Then this regular expression is expanded to all the possible string that match this regexp like
\begin{verbatim}
delete a file README.md
remove a file README.md
delete a file Makefile
remove a file Makefile
...
\end{verbatim}

And then all these strings are compared with the user's specification like
``\verb|del REA|'',
and if a matche is found,
this is translated to
``\verb|delete file README.md|''.

If ``\verb|destroy|'' should also be used for the spec,
the spec can be modified to 
\stt{(delete|remove) a (\#{file})}.

Any kind of specs in any language can be used for the specification.
For example,

\begin{verbatim}
  \#{file}を(消す|消去する)
  /bin/rm $1
\end{verbatim}

can be  used for Japanese users, who might want to delete
one of the files by specifying ``消す''.
(消す means 'delete' in Japanese).

\subsection{Generating help menu entries}

@@

\subsubsection{Phase 1: Generating a state transition diagram from a regular expression}

@@

\subsubsection{Phase 2: Generating texts from a state transition diagram}

@@

\subsection{Generate-and-Filter}

@@

\subsection{Approximate pattern matching by shifter algorithm}

簡潔に書けるか?

\subsection{Sharing database on the Web}

The data used in {\GH} are represented as ``{\SB}'' documents.
%
{\SB} is a general-purpose real-time Wiki system for data sharing.
{\SB} users can edit the contents of Wiki pages directly
on Web browsers just like text editors,
using simple markup symbols similar to MarkDown\footnote{markdown}
and other markup languages.

For {\GH}, database entries like the following

% \begin{figure}[htb]
% \begin{verbatim}
% \end{verbatim}
% \centerline{\includegraphics[width=40mm]{figures/xxxxx}}
% \caption{ssss}
% \label{xxxxx}
% \end{figure}

This page describes the usage of \qtt{git diff}, and
the page contains command specifications in {\EH} format
in addition to the description of the command.
%
% Specs and command lines are specified with a special symbol, and
% all other documents can be written just like standard manuals and help documents.

@@

On text editors and Unix shells,
``text completion'' has been available for a long time.
%
When a user types the TAB key after typing \qtt{la} on the Unix shell,
\qtt{latex}, \qtt{latex}, and other commands are shown as candidates.
When a user types \qtt{ls RE} and types the TAB key,
Unix shell checks the directory, find the \tt{README.md} file, and
replace the user's input with \qtt{ls README.md}.
This behavior is called ``text completion'', and many variations of
this idea have been proposed and adopted in text editors and command line editors.

@@

% 賢い補完
Little's system\cite{Little:2006:TKC:1166253.1166275}
generates a complete JavaScript code snippet from keyword fragments.
For example,
\qtt{ActiveDocument .PageSetup .LeftMargin = InchesToPoints(2)}
can be generated from keywords like
\qsf{left},
\qsf{margin},
\qsf{4}, and
\qsf{inches}.
The system generates the code using a template database and heuristics
for the target system.
It is useful for a special environment, but
users of the system cannot modify the algorithm or the database
even when appropriate suggestions cannot be give by the system.

@@

Han's Abbreviation Completion system\cite{Han:2009:CCA:1747491.1747530}
can generate a code snippet from abbreviation strings give by the user.
For example, a snippet like \qtt{chooser. showOpenDialog()}
can be generated from the keyword
\qsf{ch} and\qsf{opn}, using the code database and HMM.
It can be very useful as a shorthand for handling long names,
but users should have a vague knowledge about the correct names
(e.g. \qtt{chooser}, \qtt{dialog}),
and large code example corpus should exist before

>>>>

\usepackage{here} % [H]とするとその場所に配置されるらしい

@@

\begin{figure}[h]
  \includegraphics[width=9cm,bb=0 0 1000 600]{figures/githelp_e2.png}
  \caption{Invoking {\GH}.}
  \label{bash1}
\end{figure}

Here, various candidate entries with
descriptios and command strings are listed.
One of the entries says ``Compare README.md with the one from 2 versions before''.
% which means ``to compare \tt{README.md} with the one from 2 versions before.''
%
If the user thinks that that's what he wants to do,
he can select the entry by selecting it by typing arrow keys
and type the enter key.
Then the user's input string is replaced by the right command string
that satisfies the user's need.

A description like ``2 days ago'' is also shown in the candidate list.
This means that the user can use the same string ``\tt{git RE 2}''
for getting the \tt{README.md} file of the day before yesterday.
The command,
``{\fontsize{9pt}{0pt}\selectfont\verb|$ git diff '@{2 days ago}' README.md|}'',
is difficult to remember,
but users can do the same thing only by saying \sqtt{RE} and \sqtt{2}.

A Japanese \stt{git} user can do the same thing just like
English-speaking users.

\begin{figure}[H]
  % \includegraphics[width=10cm,bb=0 0 1290 866]{figures/githelp1.png}
  \includegraphics[width=12cm,bb=-100 -100 1190 766]{figures/githelp1.png}
  \caption{Invoking {\GH}.}
  \label{bash2}
\end{figure}

If the user wants to know more about the command line options,
he can click the
\raisebox{-2pt}{\includegraphics[height=11pt,bb=0 0 200 200]{figures/info-xxl.png}}
button and browse the Wiki page.
The page can be edited by any user, and

\begin{figure}[htb]
\begin{verbatim}
\end{verbatim}
% \centerline{\includegraphics[width=100mm,bb=0 0 1428 1288]{figures/scrapbox1.png}}
\centerline{\includegraphics[width=100mm,bb=-50 -50 1000 900]{figures/scrapbox1.png}}
\caption{A {\SB} page for \tt{git diff}.}
\label{scrapboxpage}
\end{figure}

@@

\subsection{ExpandHelp}

@@

\begin{quote}
  \textbf{description}: \\
  \stt{Compare (\#\{files\}) with the one from (1|2|3|4) versions before}\\
  \textbf{command}: \\
  {\fontsize{9pt}{0pt}\selectfont\verb|git diff $(git rev-list -n #{$2} HEAD -- #{$1})^ -- #{$1}|}
\end{quote}

The first regular expression, the description part,
is for generating texts like
\sqsf{Compare README.md with the one from 1 versions before}, 
\sqsf{Compare index.html with the one from 2 versions before}, etc.,
and the second part, command part,
is used to generate a command to execute a \tt{git} command.
In the first example, \sqsf{README.md} and \sqsf{1}
match the first and second parentheses of the regular expression, and
these values are assigned to \tt{\$1} and \tt{\$2}
for the command part, generating a command
``{\fontsize{9pt}{0pt}\selectfont\verb|$ git diff $(git rev-list -n #{$2} HEAD -- #{$1})^ -- #{$1}|}''.

The description part can be written in any natural language.
For example,

\begin{quote}
  \stt{(\#\{files\})を(1|2|3|4)個前のものと比較する}
\end{quote}

can be used for Japanese users.
In this case,
\sqsf{README.mdを1個前のものと比較する},
\sqsf{README.mdを2個前のものと比較する}, etc.
are used for theh matching.

@@

%% \subsection{(section written for GitHelp)}
%% 
%% {\EH} is a general-purpose flexible help generation system
%% that has the following characteristics.
%% 
%% \begin{itemize}
%% \item Use description-execution pairs for the translation
%% \item Standard regular expression is used for the specification of the description
%% \item The specification RegExp is expanded and filtered by the user's input string
%%   real-time
%% \end{itemize}
%% 
%% An example of the desc-exec pair can be the following:
%% 
%% \begin{verbatim}
%%   (delete|remove) a (#{file})
%%   /bin/rm $2
%% \end{verbatim}
%% 
%% ``remove \verb|README.md|''
%% into
%% ``\verb|rm README.md|
%% 
%% First, the spec like \stt{\#\{file\}} is expanded to a list of filenames like
%% \verb+README.md|Makefile|test.c+,
%% and the spec string becomes
%% ``\verb+(delete|remove) a file (README.md|Makefile|test.c)+''.
%% Then this regular expression is expanded to all the possible string that match this regexp like
%% \begin{verbatim}
%% delete a file README.md
%% remove a file README.md
%% delete a file Makefile
%% remove a file Makefile
%% ...
%% \end{verbatim}
%% 
%% And then all these strings are compared with the user's specification like
%% ``\verb|del REA|'',
%% and if a matche is found,
%% this is translated to
%% ``\verb|delete file README.md|''.
%% 
%% If ``\verb|destroy|'' should also be used for the spec,
%% the spec can be modified to 
%% \stt{(delete|remove) a (\#{file})}.
%% 
%% Any kind of specs in any language can be used for the specification.
%% For example,
%% 
%% \begin{verbatim}
%%   \#{file}を(消す|消去する)
%%   /bin/rm $1
%% \end{verbatim}
%% 
%% can be  used for Japanese users, who might want to delete
%% one of the files by specifying ``消す''.
%% (消す means 'delete' in Japanese).

\subsubsection{Generating help menu entries}

@@

\paragraph{Phase 1: Generating a state transition diagram from a regular expression}

@@

\paragraph{Phase 2: Generating texts from a state transition diagram}

@@

\subsubsection{Generate-and-Filter}

@@

\subsubsection{Approximate pattern matching by shifter algorithm}

The ``shifter algorithm''\cite{Wu:1992:FTS:135239.135244}
is a simple and efficient
text search algorithm which has interesting features
not found in more common pattern matching algorithms like
KMP\cite{KMP}, Boyer-Moor\cite{Boyer:1977:FSS:359842.359859}, etc.

When a user wants to find a word \qsf{README} in a text,
he can use a patter matching state machine like below,
where the gray circle denotes that the state is active.

\begin{figure}[h]
\includegraphics[width=70mm,bb=0 0 439 73]{figures/readme1.pdf}
\caption{A state machine for \qsf{README}.}
\label{readme1}
\end{figure}

Initially, only the leftmost node is active, but when the
state machine receives \qsf{R}, both the first and the second node become active
and the activation state will change to the following pattern.

\begin{figure}[h]
\includegraphics[width=70mm,bb=0 0 439 73]{figures/readme2.pdf}
\caption{After receiving \qsf{R}.}
\label{readme2}
\end{figure}

When \qsf{README} is given to the state machine,
the rightmost node becomes active.

\begin{figure}[h]
\includegraphics[width=70mm,bb=0 0 439 73]{figures/readme3.pdf}
\caption{After receiving \qsf{README}.}
\label{readme3}
\end{figure}

Although this state machine is a nondeterministic finite automata (NFA),
only 10 bits are required to represent the active/inactive states of the nodes,
meaning that the whole states can be represented by a single integer value.
Also,
the state transition can be calculated by a simple combination of
logic and bit shift operations.

%% We will describe how the pattern matching can be performed using a C code.
%% 
%% First, a variable for current state is
%% set to \stt{0x80000000}, representing the initial pattern
%% shown in Figure \ref{readme1}.
%% 
%% {
%% \scriptsize
%% \begin{verbatim}
%%  #define INITPAT 0x80000000
%%  int state = INITPAT;
%% \end{verbatim}
%% }
%% 
%% When character \qsf{r} is received, the MSB will be shifted to the right
%% by one bit, and logical OR is calculated with the initial value, \stt{0x80000000}.
%% Since the 7th node also accepts \qsf{r}, it should also be shifted.
%% The state transition can be described like below.
%% 
%% {
%% \scriptsize
%% \begin{verbatim}
%%  mask['r'] = 0x82;
%%  state = INITPAT | ((state & mask['r']) >> 1);
%% \end{verbatim}
%% }
%% 
%% The shift ``mask'' value can be easily calculated from the given
%% pattern string beforehand.
%% 
%% {
%% \scriptsize
%% \begin{verbatim}
%%   int maskpat;
%%   init(pat){
%%     maskpat= INITPAT;
%%     for(char *s=pat;*s;s++){
%%       mask[*s] |= maskpat;
%%       maskpat >>= 1;
%%     }
%%     acceptpat = maskpat;
%%   }
%% \end{verbatim}
%% }
%% 
%% The pattern matching function can be described like below.
%% 
%% {
%% \scriptsize
%% \begin{verbatim}
%%  match(s){
%%    int state = INITPAT;
%%    for(s=text;*s;s++){
%%      state = INITPAT | ((state & mask[*s]) >> 1);
%%    }
%%    return ((state & acceptpat) != 0);
%%  }
%% \end{verbatim}
%% }

\subsubsection{Approximate pattern matching using the shifter algorithm}

The state machine shown in Figure \ref{readme1} can accept only one pattern
(\sqsf{README}), but
it can be easily expanded to detect texts which contain a word
similar to the pattern (e.g. \sqsf{READY}).

%   *  ** 
%  risto rante
%  restaurant
\begin{figure}[htb]
\begin{verbatim}
\end{verbatim}
\centerline{\includegraphics[width=40mm,bb=0 0 104 51]{figures/readme-mismatch.pdf}}
\caption{Matching error between \qsf{README} and \qsf{REDDY}.}
\label{readme-reddy-mismatch}
\end{figure}

Adding three more states to Figure \ref{readme1}, we can perform more
sophisticated pattern matcher which can accept strings with
0 to 3 matching errors.

\begin{figure}[htb]
\includegraphics[width=85mm,bb=0 0 443 282]{figures/readme-ambig.pdf}
\caption{A pattern matcher accepting 0-3 errors.}
\label{shifterambig}
\end{figure}

Figure \ref{shifterambig} shows a state machine which can detect a string
which matches \sqsf{README} with 0 to 3 mismatches.
Each additional row of nodes represents a matcher with one error,
two errors, and three errors, respectively.
Vertical and diagonal transition edges are added to allow
transitions based on spelling errors.

Initially, only the bottom-left node is active.
When a character other than \sqsf{R} is detected, 
the transition labeled \sqsf{*} (wildcard) is activated,
and connected nodes become active.
At the same time, links labeled as ``$\epsilon$''
is also activated without any input character.
With these additional links, this expanded machine can detect a text which
matches \sqsf{README} with 0 to 3 errors.

% \begin{figure}[htb]
% \includegraphics[width=82mm]{figures/restaurant-ristrante.pdf}
% \caption{Accepting ``\tsf{ristorante}'' using a matcher for ``\tsf{restaurant}''.}
% \label{restaurant-ristorante}
% \end{figure}

The transition of active nodes while reading
\sqsf{REDDY} is shown in Figure \ref{restaurant-ristorante}.
After reading \sqsf{REDDY},
only the upper-right node becomes active,
denoting that \sqsf{REDDY} matches
\sqsf{README}'' with 3 matching errors.

The state transition shown in 
Figure \ref{restaurant-ristorante} looks complicated, but
the matching state can be represented by only four integer variables, and
the matching algorithm is not very different from the algorithm
shown above.

\subsubsection{Using the matcher for generate-and-filter}

We can use this approximate pattern matcher while generating
help texts by traversing the state transition machine.
%
Every time a new node is generated by traversing an edge,
matching state is calculated and stored in the generated node.
The status pattern is calculated from the status pattern
stored in the preceding node and the string associated with the edge.

% \begin{figure}[htb]
% \includegraphics[width=85mm]{figures/ristfrans1.pdf}
% \caption{A pattern matcher for ``\ttt{rist frans}''.}
% \label{ristfrans1}
% \end{figure}
% 
% \begin{figure*}[bht]
% \centerline{\includegraphics[width=110mm]{figures/gentree2.pdf}}
% \caption{Matching statuses for ``\ttt{rist frans}'' associated with text generation nodes.}
% \label{gentree2}
% \end{figure*}

% Figure \ref{ristfrans1} shows the matcher for \qtt{rist frans}\footnote{
%   A space (\qtt{ }) in the input is treated as a wildcard character.
% },
% and Figure \ref{gentree2} shows how the matching status is calculated while the
% description strings are generated from the state transition machine
% shown in Figure \ref{statemachine1}.
% The matching status at each node is calculated from the matching status
% stored in the parent node and the string associated with the edge.
% For example, when the system generates the string
% \qsf{Find a Chinese restaurant in San Francisco on Yelp.com},
% the matching status is calculated from the status data at the previous node at
% \qsf{Find a Chinese restaurant in San Francisco}, and
% the system can tell that it matches \qtt{rist frans} with two matching errors,
% as soon as the string is generated.

% The system is keeping the list of generated strings
% which match the pattern with zero to three errors
% and it displays the list with minimal number of errors
% when generating menu entries.
% 
% Since the pattern matching operation is performed at the time of text generation,
% the whole generate-and-filter calculation is quick.
% Although current version of ExpandHelp is implemented in MacRuby,
% the user can always get the result within 1 second.
% A portion of the help data in Ruby is shown in Figure \ref{helpdata}.

% \begin{figure*}[bt]
% \centerline{\includegraphics[width=146mm]{figures/04ad7dee5679450e5390821745b5a0b7.png}}
% \caption{A portion of the help data in Ruby.}
% \label{helpdata}
% \end{figure*}

\subsection{Sharing the database on the Web}

The data used in {\GH} are represented as ``{\SB}'' documents.
%
{\SB} is a general-purpose real-time Wiki system for data sharing.
{\SB} users can edit the contents of Wiki pages directly
on Web browsers just like text editors,
using simple markup symbols.

The data used for {\GH} is shown in Figure \ref{scrapboxpage}.

% \begin{figure}[htb]
% \begin{verbatim}
% \end{verbatim}
% % \centerline{\includegraphics[width=100mm,bb=0 0 1428 1288]{figures/scrapbox1.png}}
% \centerline{\includegraphics[width=100mm,bb=-50 -50 1000 900]{figures/scrapbox1.png}}
% \caption{A {\SB} page for \tt{git diff}.}
% \label{xxxxx}
% \end{figure}

This page describes the usage of \sqtt{git diff}, and
the page contains command specifications in {\EH} format
in addition to the description of \sqtt{git diff}.
%
% Specs and command lines are specified with a special symbol, and
% all other documents can be written just like standard manuals and help documents.

@@

On text editors and Unix shells,
``text completion'' has been available for a long time.
%
When a user types the TAB key after typing \sqtt{la} on the Unix shell,
\sqtt{latex}, \sqtt{latex}, and other commands are shown as candidates.
When a user types \sqtt{ls RE} and types the TAB key,
Unix shell checks the directory, find the \stt{README.md} file, and
replace the user's input with \sqtt{ls README.md}.
This behavior is called ``text completion'', and many variations of
this idea have been proposed and adopted in text editors and command line editors.

@@

% 賢い補完
Little's system\cite{Little:2006:TKC:1166253.1166275}
generates a complete JavaScript code snippet from keyword fragments.
For example,
\sqtt{ActiveDocument .PageSetup .LeftMargin = InchesToPoints(2)}
can be generated from keywords like
\sqsf{left},
\sqsf{margin},
\sqsf{4}, and
\sqsf{inches}.
The system generates the code using a template database and heuristics
for the target system.
It is useful for a special environment, but
users of the system cannot modify the algorithm or the database
even when appropriate suggestions cannot be give by the system.

@@

Han's Abbreviation Completion system\cite{Han:2009:CCA:1747491.1747530}
can generate a code snippet from abbreviation strings give by the user.
For example, a snippet like \sqtt{chooser. showOpenDialog()}
can be generated from the keyword
\sqsf{ch} and\sqsf{opn}, using the code database and HMM.
It can be very useful as a shorthand for handling long names,
but users should have a vague knowledge about the correct names
(e.g. \sqtt{chooser}, \sqtt{dialog}),
and large code example corpus should exist before
